---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Dillon Chew

## Exercise 1

Explain what you are visualizing here: Is there any relationship between seniority and legislative effectiveness in 2017? Correlation seems weak.

Put your figure here:

```{r exercise1,echo=FALSE}

ggplot(cel %>% 
           filter(year==2017) %>%
           mutate(female=recode(female, `0`="Male", `1`="Female")), 
       aes(x=les, y=seniority, color=female)) + 
    geom_point() +  
    geom_text(aes(label=st_name)) + 
    theme_bw() + 
    facet_wrap(~female, scales="free") +
    guides(color="none") + 
    labs(x="Volden and Wiseman's Legislative Effective Score (LES)", title="Seniority and LES Scores in 2017", y="Number of terms in congress") + 
    geom_smooth(method="lm")
```

## Exercise 2

Explain what you are visualizing here: Were there differences between males and female in terms of legislative effectiveness between 2011 to 2017? Does't seem to have much differences here.

Put your figure here:

```{r exercise2,echo=FALSE}

ggplot(cel %>% 
           filter(year>=2010) %>%
           mutate(female=recode(female, `0`="Male", `1`="Female")), 
       aes(x=female, y=les, color=female)) + 
    geom_boxplot() + 
    coord_flip() + 
    theme_bw() + 
    facet_wrap(~year, ncol=1) + 
    guides(color="none") + 
    labs(x="", y="Volden and Wiseman's Legislative Effective Score (LES)", title="Sex and LES Scores")
  
```

## Exercise 3

Explain what you are visualizing here: Race and Paying off Student Loans

Put your figure here:

```{r exercise3,echo=FALSE, fig.width=14, fig.height=7}

ggplot(cces %>%
           mutate(race=recode(race, 
                              `1`="White", `2`="Black",
                              `3`="Hispanic", `4`="Asian", 
                              `5`="Native American", `6`="Mixed", 
                              `7`="Others", `8`="Middle Eastern"),
                  educ=recode(educ,
                              `1`="No high school", `2`="High school graduate",
                              `3`="Some college", `4`="2-year", 
                              `5`="4-year", `6`="Post-grad"),
                  edloan=recode(edloan,
                                `1`="Yes", `2`="No")), 
       aes(x=edloan, fill=educ)) + 
    geom_bar(position="stack") + 
    facet_wrap(~race, scales="free_y", nrow=1) + 
    theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
    labs(x="Paying off Student Loan?", y="Count", 
         fill="Highest Level of Education", title="Race and Paying off Student Loans")

```

## Exercise 4

Explain what you are visualizing here: Number of Congressmen between 1973-2017

Put your figure here:

```{r exercise4,echo=FALSE}

ggplot(cel %>% 
           group_by(year) %>% 
           summarise(Democrats=sum(dem), Republicans=n()-sum(dem)) %>%
           pivot_longer(cols=Democrats:Republicans, 
                        names_to="isdem", values_to="count"), 
       aes(x=year, y=count, group=isdem, color=isdem)) + 
    geom_line() + 
    scale_color_manual(values=c("blue", "red")) + 
    labs(x="Year", y="Count", color="Political Party", 
         title="Number of Congressmen between 1973-2017") + 
    theme_bw()
```
