---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Dillon Chew



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
q1<-cces %>%
    mutate(ideo5=recode(ideo5, 
                        `1`="Very Liberal",
                        `2`="Liberal",
                        `3`="Moderate",
                        `4`="Conservative",
                        `5`="Very Conservative"))
ggplot(q1, aes(x=ideo5, fill=ideo5)) + 
    geom_bar() +
    guides(fill="none") +
    labs(x="Ideology", y="Count", title="Respondent Ideology")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
q2<-q1 %>%
    mutate(pew_religimp=recode(pew_religimp,
                               `1`="Very imp.", 
                               `2`="Somewhat imp.",
                               `3`="Not too imp.",
                               `4`="Not imp."))

ggplot(q2, aes(x=pew_religimp, fill=ideo5)) + 
    geom_bar(position="stack") + 
    labs(x="Importance of Religion", y="Count", fill="Ideology", title="Importance of Religion by Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
q3<-tibble(Semester=rep(1:6, 3),
           Student=c(rep("Amanda", 6), rep("Betty", 6), rep("Carol", 6)),
           Grade=runif(n=18, min=80, max=100))
ggplot(q3, aes(x=Semester, y=Grade, color=Student)) + 
    geom_line() +
    facet_wrap(~Student) +
    guides(color="none") +
    labs(title="Student Grades by Semester")
```
